---
title: "Stack overflow 2018 analysis"
author: "Joan Claverol Romero"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    self_contained: yes
    css: corp-styles.css
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r libraries}
if (require(pacman) == FALSE) {
  install.packages('pacman')
}
pacman::p_load(
  tidyverse,
  highcharter, 
  caret,
  modelr
)
```


# Analysis of the stack overflow survay of 2018 

## Definition of relevant paramaters

Let's define the responder profile we are interested on:

* Not a student and not coding as a hobby (why not?)
* European or USA countries (Dollars or Euros)
* Years coding (non prof. & and prof.) as a relavant opinion as more expertise
* DevType = Data or business analyst, Data scientist or machine learning specialist, Marketing or sales professional, Product manager, Educator or academic researcher

```{r import data}
public <- read_rds("../data/clean_data/data_splited.rds")
schema <- read_csv("../data/raw_data/stack-overflow-2018-developer-survey/survey_results_schema.csv")
```

## Origin of our survay participants 

We will put the focus on countries using Euros or Dollars as currency (following currecny symbols):

* EUR - Euro
* GBP - United Kingdom Pound
* USD - United states dollar
* CAD - Canadian Dollar
* AUD - Australian Dollar

```{r analysing the origin of the}
# define the relevant currancies to analyse
relevant_currencies <- c("EUR","GBP","USD","CAD","AUD")

# build the treemap
public %>% 
  dplyr::filter(CurrencySymbol %in% relevant_currencies) %>%  
  group_by(Country) %>% 
  summarise(n = n()) %>% 
  hchart("treemap", hcaes(x = Country, value = n, color = n))
```

## Analysis of countries using Euro

Overview of respondent countris using Euros and not being students:

```{r euro analysis}
euro_data <- public %>% 
  filter(CurrencySymbol == "EUR" & Student == "No") 

euro_data %>% 
  group_by(Country) %>% 
  summarise(n = n()) %>% 
  hchart("treemap", hcaes(x = Country, value = n, color = n))
```

The responders using the Europe as a currancy represents the `r round((nrow(euro_data) / nrow(public))*100,2)` % of the data. Can we find relevant factor to predict it's salary?

```{r include=FALSE}
filtered_euro_data <- public %>% 
  # filtering data by no student, no NA in converted salary or equal 0, 
  # and age between 25 and 34
  filter(Student == "No", !is.na(ConvertedSalary), 
         between(ConvertedSalary, 1, 100000), 
         Age %in% c("25 - 34 years old")) %>% 
  # extract only the developer types we are interested
  mutate(DevType.y = str_split(string = DevType.y, pattern = ";")) %>%
  unnest(DevType.y) %>% 
  filter(
    DevType.y %in% c("Data or business analyst", 
                     "Data scientist or machine learning specialist")
    ) %>% 
  nest(DevType.y) 

euro_data <- filtered_euro_data %>% 
  # select relevant variables 
  select(
    starts_with("LanguageWorkedWith_"), 
    starts_with("DevType_"),
    starts_with("CommunicationTools_"),starts_with("EducationTypes_"),
    starts_with("SelfTaughtTypes_"),starts_with("DatabaseWorkedWith_"),
    starts_with("PlatformWorkedWith_"), starts_with("FrameworkWorkedWith_"),
    starts_with("IDE_"),starts_with("Methodology_"),
    starts_with("VersionControl_"), starts_with("Gender_"),
    ConvertedSalary,
    Age, FormalEducation, UndergradMajor,
    YearsCoding, YearsCodingProf, ConvertedSalary
    ) %>% 
  # dummify the categories to introduce them in the model 
  fastDummies::dummy_columns(
    c("Age","FormalEducation", "UndergradMajor","YearsCoding",
      "YearsCodingProf")
    ) %>% 
  # unselect the variables with no dummies
  select(
    -Age, -FormalEducation, -UndergradMajor,-YearsCoding, -YearsCodingProf
    ) %>% 
  # replace all missing values by 0
  replace(., is.na(.), 0)

# create a linear model
mod <- lm(ConvertedSalary ~ ., data = euro_data)

# adding the resduals and the errors 
euro_data %<>% 
  add_predictions(model = mod, var = "resid") %>% 
  mutate(errors = ConvertedSalary - resid)
# analysing the errors
euro_data %>% 
  ggplot() +
    geom_point(aes(x = ConvertedSalary, y = resid)) +
    geom_abline(color = "red")

```

### Analysing related job opportunities

```{r}
public %>% 
  select(DevType.x)
```


### Analysing Netherlands

Filter the data based on:

* No student

```{r}
public %>% 
  filter(Country == "Netherlands", Student == "No") %>%   

```




## Analysing the amount of students in the data

```{r}
public %>% 
  select(Student) %>% 
  mutate(Student = as.factor(Student)) %>% 
  skim() %>% pander()
```







### Focus on netherlands responses

```{r}
public_netherlands <- public %>% 
  filter(Country == "Netherlands")
```

## Check for gender bias 

```{r}
public_netherlands %>% 
  group_by(Gender) %>% 
  summarise(n = n()) %>% 
  ggplot() +
    geom_col(aes(y = n, x = reorder(Gender, n)), 
             fill = "white", color = "dodgerblue4", alpha = 0.4) + 
    coord_flip() +
    xlab(label = "Gender") + ylab(label = "Count") + 
    theme_minimal() -> temp_p1
plotly::ggplotly(temp_p1)
```

# Programming lenguage analysis

## All data 

```{r}
public %>% 
  
```

